---
title: "EDA-challenge"
format: html
editor: visual
---

## EDA Challenge for Exercise 3

## Loading the Data

Prior to manipulating the data I loaded it into an R script with the following code. I chose file.choose() over a direct link out of habit. Doing this

```{r}
library(tidyverse)
library(ggplot2)
f <- file.choose()
d <- read_csv(f, col_names = TRUE)
```

Doing this created a ***tibble*** with [213 observations]{.underline} and [23 variables]{.underline}

## Challenge 1-3: Creating Variables

First step was to a create the [BSD]{.underline} (ratio of average male body mass to average female body mass), [sex_ratio]{.underline} (ratio of all male members to all female members in a species), and [DI]{.underline} (ratio of day range length to the diameter of the home range) variables in **d**. I did that by dividing the relevant columns for each new variable and loading the result as a new column in the tibble.

For [DI]{.underline}, I had to calculate the diameter from the area in kilometers squared. I first created a vector for each of the variables radii which was the square root of *HomeRange_km2* divided by pi. Then I created a new variable that was the **r** vector multiplied by 2, which multiplied two across each number.

(I also attached the tibble to make it easier to do this)

```{r}
attach(d)
d$BSD <- (Body_mass_male_mean/Body_mass_female_mean)
d$sex_ratio <- (AdultMales/AdultFemale)
r <- sqrt(HomeRange_km2)/pi
d$diameter <- r*2
d$DI <- (DayLength_km/(diameter))
```

## Challenge 2: Plotting Day-Range Length and Time Spent Moving

Second step was to plot *DayLength_km*

```{r}
attach(d)
d$BSD <- (Body_mass_male_mean/Body_mass_female_mean)
```
